\subsection*{Restrictions}

\begin{itemize}
\item In Python, a logical line is the smallest unit of code that the 
interpreter can execute, typically corresponding to a complete statement. 
A physical line, by contrast, is a single line in the source file, 
usually ending with a newline character. A logical line may span multiple 
physical lines depending on whether line joining is used.

By default, each physical line corresponds to a logical line. However, 
when a statement is too long, Python allows it to be split across multiple 
physical lines using line continuation. Python provides two ways to join 
lines: \textbf{explicit line joining} and \textbf{implicit line joining}.

\textbf{Explicit line joining} uses a backslash (\textbackslash) to join 
the current physical line with the next one, forming a single logical line. 
The backslash must be the last character on the line—no characters 
(including whitespace or comments) are allowed after it.

\begin{lstlisting}
total = 1 + 2 + 3 + \
        4 + 5
\end{lstlisting}

\textbf{Implicit line joining} occurs when expressions are enclosed in 
parentheses \texttt{()}, square brackets \texttt{[]}, or braces \texttt{\{\}}. 
Within these delimiters, line breaks are allowed without using a backslash.

\begin{lstlisting}
total = (
            1 + 2 + 3 +
            4 + 5
         )
\end{lstlisting}

Therefore, when breaking a statement across lines, you must either use a backslash for explicit continuation or wrap the expression in parentheses, brackets, or braces for implicit continuation. Unlike JavaScript, which uses automatic semicolon insertion, Python requires each line to be syntactically complete—it does not infer the end of a statement implicitly.

For details on logical lines, see the official Python documentation:
\href{https://docs.python.org/3/reference/lexical_analysis.html#logical-lines}{Python Lexical Analysis – Logical Lines}.


\item Return statements are only allowed in bodies of functions. Each return statement must appear on a single logical line.
\item Lambda expressions are limited to a single logical line.
\end{itemize}
